---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# apodR

The goal of apodR is to connect R to the NASA APOD API. The APOD API supports one image at a time. In order to suplly more than that, this package also includes creating time ranges (of less than 1000 days ata time) and some historical data in tibble format.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("eringrand/apodR")
```
## Example

This is a basic example to retrive APOD data. 

```{r example}
library(dplyr)
library(apodR)
library(DT)
get_apod() # no imputs will get today's image
```

With a little `magick` you can also save the APOD image to your computer for use later. 
This is a demostration of a picture in APOD I helped to create!
```{r}
library(magick)
library(gmp)
library(stringr)

save_image <- function(url){
  image <- try(image_read(url), silent = FALSE)
  image_name <- stringr::str_extract(m31$hdurl, "([^\\/]+$)")
  image_loc <- here::here("man/figures/README", image_name)
  if(class(image)[1] != "try-error"){
    image %>%
    image_write(image_loc)
  }
  return(image)
}

m31 <- get_apod(start_date = "2009-09-17") 
pull(m31, explanation)
save_image(m31$hdurl)
```

