---
title: "Historical APOD"
author: "Erin Grand"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Historical APOD}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Basics
The `astropoc` package contains a data set ready to be used with all the APOD information from 2007 to today.

```{r init}
library(astropic)
library(tidytext)
library(dplyr)
library(ggplot2)
library(tidytext)
library(lubridate)
library(forcats)

data("hist_apod")
str(hist_apod)
```

- `copyright` The copyright of the image if it's not in public domain.
- `date` Date of image
- `explanation` The supplied text explanation of the image.
- `hdurl` The URL for any high-resolution image for that day. Returned regardless of 'hd' param setting but will be ommited in the response IF it does not exist originally at APOD.
- `media_type` The type of media (data) returned. May either be 'image' or 'video' depending on content.
- `title` The title of the image.
- `url` The URL of the APOD image or video of the day.

## Example: Word Count 

My favorite part of the APOD data is working with the `explanation` field. There's a ton of cool text analysis you can do with it.


```{r words}
words <- hist_apod |>
  select(date, title, explanation, media_type) |>
  mutate(year = lubridate::year(date)) |>
  tidytext::unnest_tokens(word, explanation, token = "words") |>
  anti_join(tidytext::stop_words) 

head(words)
```

```{r fig.height=4, fig.show='hold', fig.width=5}
word_counts <- words |>
  count(word, sort = TRUE) |>
  top_n(10, n)  |>
  mutate(word = fct_rev(fct_inorder(word)))

word_counts |>
  ggplot(aes(x = n, y = word, xend = 0, yend = word, color = word)) +
  geom_segment(size = 1.1, show.legend = FALSE) +
  geom_text(aes(label = n), hjust = -0.25, show.legend = FALSE) +
  labs(x = "", y = "",
       title = "APOD Word Counts",
       subtitle = "2007-2017") +
  theme_classic(base_size = 14) +
  theme(axis.title.x = ggplot2::element_blank(),
        axis.text.x = ggplot2::element_blank(),
        axis.ticks = ggplot2::element_blank(),
        axis.line = ggplot2::element_blank()) +
  scale_x_continuous(limits = c(0, max(word_counts$n) + 400)) 
```

## Example: Frequncy of Words by Year
```{r fig.height=3, fig.show='hold', fig.width=5}
plot_dat <- words |>
  add_count(year) |>
  rename(nwords = n) |>
  count(year, nwords, word, sort = TRUE) |>
  mutate(freq = n / nwords) |>
  filter(word %in% c("galaxy", "planet", "sun", "nebula")) |>
  arrange(year)

plot_dat |> 
  ggplot(aes(x = year, y = freq, color = word)) +
  geom_line() +
  scale_x_continuous(breaks = seq(2007, 2017, 2), limits = c(2007, 2018)) +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Year", y = "Frequency of Word", 
       title = "Comparing Frequencies over the Years",
       subtitle = "APOD 2007 - 2017") +
  theme_classic(base_size = 14) 
```


